---
title: "DM2 Pratical Assignment 2"
author: "Pedro Belém, Rui Fonseca"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

## Find basic movie information
To make this feature we first made a function that given a string it will query that string to imdb and return a list with the id's of the movies found.

```{r}
searchTitle <- function(query, max=200){
  query <- URLencode(query)
  resultPage <- read_html(str_interp("http://www.imdb.com/find?q=${query}&s=tt"))
  filmList <- html_nodes(resultPage, ".findList")
  filmList <- html_children(filmList)
  listCount <- length(filmList)
  if(!listCount){ 
    return(NULL)
  }
  if(max < listCount){
    listCount = max
  }
  movieList <- c()
  for(i in 1:listCount){
    movieAnchor <- html_children(html_children(filmList[i])[2])[1]
    movie <- str_split(movieAnchor,"/")[[1]][3]
    movieList <- c(movieList, movie)
  }
  return(movieList)
}
```

After having a way to find the id of the movie we which to get information of, we can use the imdb movie page to get various details, so we made various functions to get specific informations but to prevent that we request the movie page various times we made it possible to pass the page to to the function. This way we only need to request the page once even if we need various details.  

```{r}
getTitle <- function(movieID, page=NULL){
  if(is.null(page)){
    page <- read_html(str_interp("http://www.imdb.com/title/${movieID}"))
  }
  return(html_text(html_nodes(page, "#title-overview-widget h1")))
}

getYear <- function(movieID, page=NULL){
  if(is.null(page)){
    page <- read_html(str_interp("http://www.imdb.com/title/${movieID}"))
  }
  return(page %>% html_nodes("#titleYear a") %>% html_text() %>% as.numeric())
}

getCast <- function(movieID, page=NULL){
  if(is.null(page)){
    page <- read_html(str_interp("http://www.imdb.com/title/${movieID}"))
  }
  return(page %>% html_nodes("#titleCast .itemprop span") %>% html_text())
}


getDirector <- function(movieID, page=NULL){
  if(is.null(page)){
    page <- read_html(str_interp("http://www.imdb.com/title/${movieID}"))
  }
  return(html_nodes(page, ".credit_summary_item .itemprop")[1] %>% html_text())
}
```

To get all the details of a movie, in a vector we have this function
```{R}
getDetails <- function(movieID){
  link <- str_interp("http://www.imdb.com/title/${movieID}")
  page <- read_html(link)
  description <- c(link=link, title=getTitle(movieID,page), year=getYear(movieID,page),
                   director=getDirector(movieID,page), cast=getCast(movieID,page))
  return(description)
}
```

## Collect all the reviews of a movie
We didn't find any IMDB url that showed all reviews of a movie but it is possible to choose the number of the reviews we wanted. A way to do it would be to first find how many reviews the movie has and then query that many reviews. However we found a hyperlink in the reviews page that finda all the reviews (but not with the full information) and by changing the url we can get all the reviews. The page then has all the reviews in text and the score so we could extract it. We made a function that receives a movie id and returns a list of reviews (text and score). We also added the title of the review to the text because it could be important.

```{R}
extractScore <- function(html_node) {
  scoreImg <- html_node(html_node, "h2+ img")
  if(!is.na(scoreImg)){
    score <- html_attr(scoreImg, "alt")
    score <- as.integer(str_split(score,"/")[[1]][1])
  }
  else{
    score <- NA
  }
  return(score)
}

getReviews <- function(movie_id, count = 0){
  indexReviewsPage <- read_html(str_interp("http://www.imdb.com/title/${movie_id}/reviews-index?"))
  showAllPartialUrl <- html_nodes(indexReviewsPage, "table+ table a+ a") %>% html_attr("href")
  if(count > 0){
    showAllPartialUrl <- gsub("count=(\\d)+", str_interp("count=${count}"), showAllPartialUrl)
  }
  showAllReviewsPartialUrl <-gsub("-index","", showAllPartialUrl)
  showAllReviewsUrl <- str_interp("http://www.imdb.com/title/${movie_id}/${showAllReviewsPartialUrl}")
      
  
  listReviewsPage <- read_html(showAllReviewsUrl) 
  reviewsNodeList <- html_nodes(listReviewsPage, "#tn15content div+ p , hr+ div")
  reviews <- list()
  for(i in seq(1, length(reviewsNodeList), 2)){
    score <- extractScore(reviewsNodeList[i])          
    title <- html_text(html_node(reviewsNodeList[i], "h2"))
    text <- html_text(reviewsNodeList[i+1])
    text <- paste(title, text, "\n")
    reviews$scores <- c(reviews$scores, score)
    reviews$text <- c(reviews$text, text)
  }
  return(reviews)
}

```